Musical analysis

Sample based music has an 
Samples of Motown backing bands, pop stars, and jazz legends can be stitched together to create a collage of sound combining all of their talents.
Sampling has the potential to make music that was never possible before.
Out of a musician's life work, the sampler can choose a 10 second snippet that perfectly
Condensing hours and hours of recording time, studios across the globe and talents of all sorts.

While some artists have made sampled based masterpieces, they take considerable ammount of time.
The issue
The goal of this project is to reduce almost all of the manual labor associated with sampling.
The process should ideally be simply listening to music, choosing what sounds good, and then
In reality lots of time is spent tuning samples, matching beats, and matching chords.

Phase vocording works to solve this problem, it nessesarily introduces digital artifacts.
Although subtle, these artifacts can break the suspension of disbelief holding together the dream that Madonna and James Brown really did record together.
Rather than using computers to directly manipulate audio, this work intends to do an intense analysis on a sample library, beyond the scope of humans, to find pairings for samples.
While more digital processing has been done to the audio than probably any other production, the actual audio signal path could be completely analog. 


Tuning
This is a constant. We assume the song is short enough and was transcoded though suitable means so it does not detune while it is being played. 

Frequency estimation
amplitude estimation

Tempo detection
Approximating the tempo
Onset detection
Autocorrelation
Then use wavelets to detect self similarity

Tempo detection happens in three steps.
First we convert the audio signal into an ``onset'' signal, which is a positive signal whose amplitude correlates to to how much the signal is changing at that point. This signal is high when the amplitude or pitch of the signal suddenly changes, which would be a ``beat.''
Next we approximate the tempo by looking for the frequency of self simiarity in this onset signal.
Finally, we fine tune this approximation to get function for the tempo that minimizes the ammount of onset information that occurs off-beat.

Onset signal

Using an analysis by [], we are going to 
We window the audio signal into frames.
We use the previous two frames to linearly predict what the third frame should be.
If the signal is changing this third frame will be different than the previous two.
So we simply calculate the euclidean distance between our predicted frame and the actual frame.

Approximating the signal

A tempo in music is the frequency at which the music exhibits some sort of self similarity. Self similariy on music exists on many levels. There is repeating verse structure - 16 bars, repeating chord progressions - 4 bars, repeating drum beats - 1 bar, and the beat itself - 1 quarter note.
In order to divide up a song as finely as to display its harmonic and rythmic features want to find the minimum frequency at which the song exhibits self similarity. 

Fine tuning the approximation

Many modern music recordings are 

While in most cases playing to a click or quantized electronic music has a perfectly consistent tempo, we would like to include music played live, where the tempo can slowly shift or change
Series approximation with wavelets?
Fourier series?
Polynomial approximation
Approximation
b(t) = a_0+a_1t+...
b(t) = a_0 + a_1cos(
Find coeffiecient, then next coefficient must have average of first ...
Most songs will have 0 higher order coefficients
But those that fluctuate will not.

Chords
Using the tempo and the one as a guide,
divide the song according to beat positions

Equal loudness contour
Normalizing energy per beat.
Wrap to an octave (hard quantize, filter out very low signals)

Finding songs that work together
Scale polynomials (tune) and find starting point,
so that fluctation of beat over length is negligible

Recurrent neural nets and PU Learning
Train the NN to learn the difference between positive examples
(real songs)
and songs that have been built like above
The samples should be
Punish false positives less than false negatives.
So that all positive examples are learned, and some negative ones will bleed through
Search for ones that do indeed bleed through.

